### 2016-05-31 syntax.tex
hacking syntax

@@

\heading{Soundness of hash-based filters.} \tsnote{To do.  Note that it makes sense to consider soundness both in the public and private hash setting.  NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g. set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}

@@

\heading{Soundness for mutable hash-based filters. } \tsnote{To do.  Same comments as for the simple case, only it's more complicated here what it means to violate soundness.}

>>>>

\newcommand{\ExpFPSecHash}[2]{\mathrm{Exp}^{\mathrm{fp\mbox{-}prv}}_{#1}(#2)}
\newcommand{\ExpFPPubHash}[2]{\mathrm{Exp}^{\mathrm{fp\mbox{-}pub}}_{#1}(#2)}
\newcommand{\ExpFP}[2]{\mathrm{Exp}^{\mathrm{fp}}_{#1}(#2)}

@@

\heading{FP-security of hash-based filters.} \tsnote{Write text.  Note that it makes sense to consider soundness both in the public and private hash setting.  NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g. set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0\\

\medskip
\experimentv{$\ExpFPPubHash{S,B}{A}$}\\
$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
$M \gets \Init^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
if $M = \bot$ then Ret $\bot$\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$.  {\bf Top:} when the hash functions are private.  {\bf Bottom:} when the hash functions are public.}
\label{fig:fp-filter}
\end{figure}

\heading{Privacy of hash-based filters.} \tsnote{To-do.}

@@

\heading{Soundness for mutable hash-based filters. } \tsnote{To do.  Same comments as for the simple case, only it's more complicated here because I have no idea what soundness even means in this setting.  Might generically specify two tests as part of the syntax, one for correctness and one for soundness?}

\heading{Privacy of hash-based filters.} \tsnote{To-do.}
